Sensitivity of He Flames in X-ray Bursts to Nuclear Physics

### 2023-06-06 xrb5/paper.tex
update and address comments

@@

%======================================================================
% Abstract and Keywords
%======================================================================
\begin{abstract}
Through the use of axisymmetric 2D hydrodynamic simulations, we further investigate laterally propagating flames in X-ray bursts (XRBs). Our aim is to investigate the sensitivity of a propagating helium flame to different nuclear physics.  Using the \castro\ simulation code, we confirm the phenomenon of enhanced energy generation shortly after a flame is established after by adding ${}^{12}\mbox{C}(\mbox{p}, \gamma) {}^{13}\mbox{N}(\alpha, \mbox{p}){}^{16}\mbox{O}$ to the network, in agreement with the past literature. This sudden outburst of energy leads to a short accelerating phase, causing a drastic alteration in the overall dynamics of the flame in XRBs. % that is crucial to accurately modeling the flame dynamics in XRBs. 
%We discover that the approximations made in the traditional networks like {\tt aprox13} are still accurate in the context of XRB, but insufficient to correctly model the flame propagation due to the missing rates. 
Furthermore, we investigate the influence of different plasma screening routines on the propagation of the XRB flame. We finally examine the performance of simplified-SDC, a novel approach to hydrodynamics and reaction coupling incorporated in \castro, as an alternative to operator-splitting.

@@

Since the timescale of accretion between each burst is in the order of $10^4$ secs while the rise time is in the order of $\sim 1 - 10$ sec \citep{Parikh_2013}, it is unlikely for the same thermodynamic condition to exist on the entire surface of the neutron star to start burning simultaneously \citep{Shara_1982}. Therefore, nuclear ignition is likely to begin in a localized region, and spread to the rest of the neutron star \citep{Spitkovsky_2002}. This asymmetrical burning leads to modulations in the observed flux during the rotation of neutron stars, which causes asymmetrical surface brightness during XRBs \citep{strohmayer_2009}. This explains burst oscillation behavior, a millisecond period variation of XRB intensity during rise time, and the double-peak light curve for non-photospheric-radius-expansion XRBs discovered and supported by observational data \citep{Altamirano_2010,Chakraborty_2014,Bhattacharyya_2006, Kaaret_2007,Smith_1997}.

@@

In the past, numerous successes have been achieved in studying the properties of neutron stars and the mechanisms of XRBs using numerical simulations.
One-dimensional simulations can determine the nucleosynthesis, study the rp-process, estimate burst duration, and predict the light curve of XRBs by assuming spherical symmetry \citep{Woosley_2004,Johnston_2018,Meisel_2018,Johnston_2020}. On the other hand, multi-dimensional simulations are conducted to study the behavior of lateral flame propagation and flame structure for their nontrivial contributions to the structure of the XRB light curve \citep{eiden:2020,harpole:2021,cavecchi:2013,Cavecchi_2015,Cavecchi_2016}.

@@

We use {\castro} \citep{castro,castro_joss}, an open-source, adaptive mesh, astrophysical radiation hydrodynamics simulation code, to perform all the simulations discussed in this manuscript. The reaction networks,
integrators, equation of state \citep{timmes_swesty:2000}, thermal neutrino losses \citep{neutrino}, and conductivities
\cite{Timmes00} are contained in the related {\microphysics} package \citep{starkiller}.

@@

During an XRB, nucleosynthesis involves more than a thousand isotopes \citep{Woosley_2004,Koike_2004}. However, due to computational constraints, most multi-dimensional simulations incorporate fewer than 20 isotopes. Thus, this manuscript aims to understand how the different approximations used in the nuclear physics impact on the lateral thermonuclear flame in XRBs.

@@

In \citet{eiden:2020,harpole:2021}, we used the 13-isotope $\alpha$-chain network, {\tt aprox13} \citep{timmes_aprox13} network.  We'll
use that as the reference network for comparison here.  
%Visuals can be found in Figure \ref{fig:networks}. 
The main feature of {\tt aprox13} is the $(\alpha, \mbox{p})(\mbox{p}, \gamma)$ approximation that eliminates the intermediate nuclei involved in $(\alpha, \mbox{p})(\mbox{p}, \gamma)$ by
assuming proton equilibrium in the reactive flow.
As a result, {\tt aprox13} has a total of 13 isotopes and 31 rates. Nevertheless, the $(\alpha, \mbox{p})(\mbox{p}, \gamma)$ approximation becomes less accurate for temperatures $\gtrsim 2.5 \times 10^9$ K, potentially affecting the energy generation rates.  An illustration of this can be found in \cite{pynucastro2} (see Figure 6 there).

@@

The {\tt subch\_full} was introduced in Appendix B of \cite{castro_simple_sdc} for simulating He burning in sub-Chandrasekhar mass white dwarfs (hence, the {\tt subch} prefix). {\tt subch\_full} network has three main modifications compared to {\tt aprox13} network. First {\tt subch\_full} explicitly includes the intermediate nuclei for the $(\alpha, \mbox{p})(\mbox{p}, \gamma)$ sequence.  Second, it has
a better representation of carbon and oxygen burning by including the endpoint nuclei of the difference branches: ${}^{12}\mbox{C}({}^{12}\mbox{C}, \mbox{p}) {}^{23}\mbox{Na} (\mbox{p}, \gamma) {}^{24}\mbox{Mg}$, ${}^{12}\mbox{C} ({}^{12}\mbox{C}, \mbox{n}){}^{23}\mbox{Mg} (\mbox{n}, \gamma) {}^{24}\mbox{Mg}$,  ${}^{16}\mbox{O} ({}^{16}\mbox{O}, \mbox{n}){}^{31}\mbox{S} (\mbox{n}, \gamma) {}^{32}\mbox{S}$, and ${}^{16}\mbox{O} ({}^{12}\mbox{C}, \mbox{n}){}^{27}\mbox{Si} (\mbox{n}, \gamma) {}^{28}\mbox{Si}$.  Since the neutron capture processes on the intermediate nuclei happen at a fast timescale, the rates
including neutrons are approximated by assuming the subsequent neutron capture is instantaneous as ${}^{12}\mbox{C} ({}^{12}\mbox{C}, \gamma) {}^{24}\mbox{Mg}$,  ${}^{16}\mbox{O} ({}^{16}\mbox{O}, \gamma) {}^{32}\mbox{S}$, and ${}^{16}\mbox{O} ({}^{12}\mbox{C}, \gamma) {}^{28}\mbox{Si}$, and the network does not include neutrons. We also note that their reverse rates are not included due to their negligible effects at $T \sim 10^9$ K.  Finally, we included the additional rates ${}^{14}\mbox{N}(\alpha,\gamma){}^{18}\mbox{F}(\alpha, \mbox{p}){}^{21}\mbox{Ne}$ and ${}^{12}\mbox{C}(\mbox{p}, \gamma) {}^{13}\mbox{N}(\alpha, \mbox{p}){}^{16}\mbox{O}$, discussed in \cite{Shen_2009, Weinberg_2006,Karakas_2008} to bypass the comparatively slow ${}^{12}$C $\alpha$-capture process, ${}^{12}\mbox{C} (\alpha, \gamma) {}^{16}\mbox{O}$, when $T \gtrsim 10^9$ K. The first $\alpha$-capture process on ${}^{14}\mbox{N}$ and ${}^{18}\mbox{F}$ led to the production of protons that can be used for the $\alpha$ chain process on ${}^{12}\mbox{C}$. When $T \gtrsim 10^9$ K, ${}^{12}\mbox{C}(\mbox{p}, \gamma) {}^{13}\mbox{N}(\alpha, \mbox{p}){}^{16}\mbox{O}$ is expected to dominate the reactive flow towards the heavy $\alpha$ chain nuclei, which can lead to a completely different end-stage composition \citep{Weinberg_2006}. Since these additional rates leave ${}^{21}\mbox{Ne}$ as the endpoint, ${}^{22}\mbox{Na}$ is added to connect all the nuclei. With all the modifications, {\tt subch\_full} has 28 isotopes and 107 rates.

{\tt subch\_full\_mod} is identical to the {\tt subch\_full} network, except that the ${}^{12}\mbox{C}(\mbox{p}, \gamma) {}^{13}\mbox{N}(\alpha, \mbox{p}){}^{16}\mbox{O}$ and its reverse reactions are turned off. This is done to explore the significance of these two rates, as described in \cite{Shen_2009, Weinberg_2006}.

@@

Lastly, we present {\tt subch\_simple} network, a simplification of {\tt subch\_full} network that would resemble a more similar network to {\tt aprox13}. The network omits a total of six nuclei, namely ${}^{35}\mbox{Cl}$, ${}^{39}\mbox{K}$, ${}^{43}\mbox{Sc}$, ${}^{47}\mbox{V}$, ${}^{51}\mbox{Mn}$, and ${}^{55}\mbox{Co}$, using the $(\alpha, \mbox{p})(\mbox{p}, \gamma)$ approximation. The reverse rates of all ${}^{12}\mbox{C} + {}^{12}\mbox{C}$,  ${}^{16}\mbox{O} + {}^{16}\mbox{O}$, and ${}^{16}\mbox{O} + {}^{12}\mbox{C}$ are removed since they are not present in {\tt aprox13}. All the forward and reverse rates of ${}^{12}\mbox{C} + {}^{20}\mbox{Ne}$ , ${}^{23}\mbox{Na}(\alpha, \gamma){}^{27}\mbox{Al}$, and ${}^{27}\mbox{Al}(\alpha, \gamma){}^{31}\mbox{P}$ are also removed to simplify the network.After the simplifications, we now have 22 isotopes and 57 rates. See the bottom panel of Figure \ref{fig:networks} for visualization.

@@

Plasma screening is the enhancement of nuclear reaction rates due to the Coulomb coupling of the surrounding plasma electrons and ions. Plasma screening plays an important role in accurately calculating nuclear reaction rates in dense regions,
and there are many approximations for it in the literature, but these are not
often explored in real simulations.

A reaction rate cross section, $\sigma$, takes the form:
\begin{equation}
    \sigma(E) = \frac{S(E)}{E} e^{-2\pi \eta}
\end{equation}
where $S(E)$ contains the details of the nuclear physics, $E$ is the energy of particle collisions in the center-of-mass frame, and $\eta$, accounts for Coulomb barrier penetration due to quantum effects \citep{Newton2007}. The reaction rate, $R_{\textrm{th}}$, is found by integrating the cross-section over the Maxwellian velocity distribution.  If the nuclei involved in the reaction are present in a high-density region that is permeated with plasma particles, the strength of the Coulomb barrier would be reduced due to the plasma screening effect since the effective charge of the fusing nuclei are reduced. The screening enhancement factor is usually expressed as
\begin{equation}
    F_{\textrm{scr}} = \exp{(h)}
\end{equation}
where $h$ is a function that characterizes the screening magnitude. Therefore, the overall screened nuclear reaction rate is defined as
\begin{equation}\label{Eq:screened_rate}
    R_{\textrm{scr}} = F_{\textrm{scr}}R_{\textrm{th}}
\end{equation}

@@

{\tt SCREEN5} is the name of a widely-circulated screening routine (originally written in Fortran) that was the original screening routine used by \castro.
The overall procedure of {\tt SCREEN5} is summarized in the appendix of \cite{Wallace:1982}. In {\tt SCREEN5}, we define $\Gamma = (2/(Z_1+Z_2))^{1/3}Z_1 Z_2 \Gamma_e$, where $\Gamma_e = e^2\sqrt[3]{(4\pi n_e/3)}/(k_BT)$ describes the thermodynamic condition at which the reaction takes place, $Z$ is the charge of the fusing nuclei, $\mu_{12}$ is the reduced mass for the two fusing nuclei, $e$ is the electron charge, $n_e$ is the electron number density, and $k_B$ is Boltzmann's constant. When the plasma screening effect is weak or $\Gamma < 0.3$, {\tt SCREEN5} utilizes the equation proposed by \cite{Graboske_1973, Dewitt_1973}, which assumes that the interacting nuclei are separated by zero distance. To account for the spatial dependence of the screening enhancement factor, a more precise description of the strong plasma screening limit is utilized when $\Gamma > 0.8$. In \cite{jancovici:1977}, a quadratic dependence of the separation distance between the interacting nuclei was shown. This idea was applied to a one-component plasma by \cite{alastuey:1978}. By following a similar procedure outlined in \cite{itoh:1979}, the screening routine for one-component plasma can be extended to a multi-component plasma, which is suitable for a general mixture of ions. Finally, a weighted average between the weak and strong screening enhancement functions is used when $0.3 < \Gamma < 0.8$, the criteria for the intermediate screening regime.

@@

The default method for coupling hydrodynamics and nuclear reactions in {\castro} is the classic Strang-splitting method \citep{strang:1968}. This operator-splitting approach considers the hydrodynamics and nuclear reactions to be independent processes. 
The overall procedure of Strang-splitting is as follows: first, the reactive part of the system is integrated over half of the timestep, $\Delta t/2$, using a standard ODE solver to determine the solution of an intermediate state, $\mathcal{U}^\star$, which is centered in time. Advection then
evolves $\mathcal{U}^\star$ through a full timestep $\Delta t$
yielding the state $\mathcal{U}^{\star\star}$.  Finally,
the second half-timestep of burning is done to obtain the final state $\mathcal{U}^{n+1}$. By applying the advection and hydrodynamic operator to an intermediate state that has already incorporated the nuclear reaction effect over $\Delta t/2$, an indirect coupling is achieved between the two operations and achieves a second-order accuracy in time.  The Strang-splitting implementation
in \castro\ was described in \cite{castro_strang}.

@@

A simplfiied-SDC algorithm was introduced in \castro\ in \cite{castro_simple_sdc}.  The simplified-SDC algorithm explicitly couples reactions and hydrodynamics by including a reactive source in the hydrodynamics
interface state prediction and including an advective source in the reaction ODE integration.  
The simplified-SDC scheme offers advantages over the traditional Strang-splitting method even though they both achieve second-order accuracy in time. Specifically, the simplified-SDC scheme provides a direct coupling between hydrodynamics and nuclear reactions, which eliminates the splitting error associated with operator splitting. It also reduces the stiffness of solving reaction equations, leading to reduced computational expenses under extreme thermodynamic conditions.  For
explosive reactive flows, it was observed that the simplified-SDC method
provides a more accurate evolution than the Strang-split method.  In this paper, we seek to understand what advantages, if any, it has for the more moderate burning in XRBs.

@@

We present a total of seven XRB simulations models using different combinations of reaction networks, time evolution methods, and screening routines. In order to investigate the sensitivity of the propagating flame to nuclear reactions, the default screening routine, {\tt SCREEN5}, and time evolution methods, Strang-splitting, are used with a variation in the networks: {\tt aprox13}, {\tt subch\_full}, {\tt subch\_full\_mod}, {\tt subch\_simple}. We replaced the {\tt SCREEN5} screening routine with {\tt CHUGUNOV2007} for the {\tt aprox13} model with Strang-splitting to investigate the difference in their performance. Lastly, in order to test the performance of the simplified SDC method, we ran two additional simulations using the two selected reaction networks, {\tt aprox13} and {\tt subch\_full}, with simplified SDC instead of Strang-splitting. The overall summary of the simulation settings is shown in Table \ref{Tab:settings}, and we will now refer to each specific model using its name.

@@

Figure \ref{fig:network_abar_50ms} shows a comparison of the mean molecular weight, $\Bar{A}$, for the four networks at $t = 50$ ms. Regions with a larger $\Bar{A}$ represents the ash of burning process which gives a rough estimate of where the burning process has already taken place. One immediate feature is the similarity of the ash structure between {\tt aprox13} and {\tt subch\_full\_mod}, as well as between {\tt subch\_full} and {\tt subch\_simple}. Unlike {\tt aprox13} and {\tt subch\_full\_mod}, there is a thicker overall ash structure on the surface indicating a much more rigorous burning process in general. The sudden increase in the ash height from $r = 5 \times 10^4$ cm to $10^5$ cm further implies a non-uniform burning has taken place, unlike the other two models. The darker color means that the ash in {\tt subch\_full} and {\tt subch\_simple} is composed of heavier nuclei suggesting a faster reactive flow burning to the heavier nuclei compared to the other two models. The ash also extends further out suggesting a faster flame speed compared to {\tt aprox13} and {\tt subch\_full\_mod}. 
The energy generation rate (shown in Figure \ref{fig:network_enuc_50ms}) shows the same trends: {\tt subch\_full} and {\tt subch\_simple} clearly possess a higher $\dot{e}_{\textrm{nuc}}$ in both magnitude and region coverage compared to the other two. 
% We continue to see the similar behavior of the 4 different simulation models in Figure \ref{fig:network_z_50ms}, which shows the velocity induced by the Coriolis force going out of the plane.

@@

In order to quantify how the flame changes over time, we look at the
density-weighted profile of temperature and energy generation rate in the burning, similar to the procedure in \citet{harpole:2021}. 
In order to filter out the burning regions, we selected cells that are in the 99th percentile for temperature or energy generation rate. A density-weighted average is then applied to temperature and energy generation rate using Equation \ref{Eq:weighted_equation}, where $\left<Q\right>_w$ is the weighted quantity, $C_{99}(Q)$ are cells where the quantity, $Q$, is in the 99th percentile, and $\rho(c_i)$ and $Q(c_i)$ are the density and the quantity in $c_i$ cell.

\begin{equation}\label{Eq:weighted_equation}
    \left<Q\right>_w = \frac{\sum\limits_{c_i}^{} \rho(c_i) Q(c_i)}{\sum\limits_{c_i} \rho(c_i)}; c_i \in C_{99}(Q)
\end{equation}

>>>>

\author[0000-0001-6191-4285]{Kiran Eiden}
\affiliation{Department of Astronomy,
University of California, Berkeley,
Berkeley, CA 94720-3411, USA}

@@

%======================================================================
% Abstract and Keywords
%======================================================================
\begin{abstract}
Through the use of axisymmetric 2D hydrodynamic simulations, we further investigate laterally propagating flames in X-ray bursts (XRBs). Our aim is to understand the sensitivity of a propagating helium flame to different nuclear physics.  Using the \castro\ simulation code, we confirm the phenomenon of enhanced energy generation shortly after a flame is established after by adding ${}^{12}\mbox{C}(\mbox{p}, \gamma) {}^{13}\mbox{N}(\alpha, \mbox{p}){}^{16}\mbox{O}$ to the network, in agreement with the past literature. This sudden outburst of energy leads to a short accelerating phase, causing a drastic alteration in the overall dynamics of the flame in XRBs. % that is crucial to accurately modeling the flame dynamics in XRBs. 
%We discover that the approximations made in the traditional networks like {\tt aprox13} are still accurate in the context of XRB, but insufficient to correctly model the flame propagation due to the missing rates. 
Furthermore, we investigate the influence of different plasma screening routines on the propagation of the XRB flame. We finally examine the performance of simplified-SDC, a novel approach to hydrodynamics and reaction coupling incorporated in \castro, as an alternative to operator-splitting.

@@

Since the timescale of accretion between each burst is in the order of $10^4$ secs while the rise time is in the order of $\sim 1 - 10$ sec \citep{Parikh_2013}, it is unlikely for the same thermodynamic condition to exist on the entire surface of the neutron star and for the entire surface to start burning simultaneously \citep{Shara_1982}. Therefore, nuclear ignition is likely to begin in a localized region, and spread to the rest of the neutron star \citep{Spitkovsky_2002}. This asymmetrical burning leads to modulations in the observed flux during the rotation of neutron stars, which causes asymmetrical surface brightness during XRBs \citep{strohmayer_2009}. This explains burst oscillation behavior, a millisecond period variation of XRB intensity during rise time, and the double-peak light curve for non-photospheric-radius-expansion XRBs discovered and supported by observational data \citep{Altamirano_2010,Chakraborty_2014,Bhattacharyya_2006, Kaaret_2007,Smith_1997}.

@@

Numerous successful numerical simulations have explored the properties of neutron stars and XRBs.
One-dimensional simulations can determine the nucleosynthesis, study the rp-process, estimate burst duration, and predict the light curve of XRBs by assuming spherical symmetry \citep{Woosley_2004,Johnston_2018,Meisel_2018,Johnston_2020}. On the other hand, multi-dimensional simulations are conducted to study the behavior of lateral flame propagation and flame structure for their nontrivial contributions to the structure of the XRB light curve \citep{eiden:2020,harpole:2021,cavecchi:2013,Cavecchi_2015,Cavecchi_2016}.

@@

We use {\castro} \citep{castro,castro_joss}, an open-source, adaptive mesh, astrophysical simulation code, to perform all the simulations discussed in this manuscript. The reaction networks,
integrators, equation of state \citep{timmes_swesty:2000}, thermal neutrino losses \citep{neutrino}, and conductivities
\cite{Timmes00} are contained in the related {\microphysics} package \citep{starkiller}.

@@

During an XRB, nucleosynthesis involves more than a thousand isotopes \citep{Woosley_2004,Koike_2004}. However, due to computational constraints, most multi-dimensional simulations incorporate fewer than 20 isotopes. Thus, this paper aims to understand how the different approximations used in the nuclear physics impact on the lateral thermonuclear flame in XRBs.

@@

In \citet{eiden:2020,harpole:2021}, we used the 13-isotope $\alpha$-chain network, {\tt aprox13} \citep{timmes_aprox13} network.  We'll
use that as the reference network for comparison here.  
%Visuals can be found in Figure \ref{fig:networks}. 
The main feature of {\tt aprox13} is the $(\alpha, \mbox{p})(\mbox{p}, \gamma)$ approximation that eliminates the intermediate nuclei involved in $(\alpha, \mbox{p})(\mbox{p}, \gamma)$ by
assuming proton equilibrium in the reactive flow.
As a result, {\tt aprox13} has a total of 13 isotopes and 31 rates. Nevertheless, the $(\alpha, \mbox{p})(\mbox{p}, \gamma)$ approximation can become less accurate for temperatures $\gtrsim 2.5 \times 10^9$ K, potentially affecting the energy generation rates.  An illustration of this can be found in \cite{pynucastro2} (see Figure 6 there).

@@

The {\tt subch\_full} network was introduced in Appendix B of \cite{castro_simple_sdc} for simulating He burning in sub-Chandrasekhar mass white dwarfs (hence, the {\tt subch} prefix). {\tt subch\_full} network has three main modifications compared to {\tt aprox13} network. First {\tt subch\_full} explicitly includes the intermediate nuclei for the $(\alpha, \mbox{p})(\mbox{p}, \gamma)$ sequence.  Second, it has
a better representation of carbon and oxygen burning by including the endpoint nuclei of the difference branches: ${}^{12}\mbox{C}({}^{12}\mbox{C}, \mbox{p}) {}^{23}\mbox{Na} (\mbox{p}, \gamma) {}^{24}\mbox{Mg}$, ${}^{12}\mbox{C} ({}^{12}\mbox{C}, \mbox{n}){}^{23}\mbox{Mg} (\mbox{n}, \gamma) {}^{24}\mbox{Mg}$,  ${}^{16}\mbox{O} ({}^{16}\mbox{O}, \mbox{n}){}^{31}\mbox{S} (\mbox{n}, \gamma) {}^{32}\mbox{S}$, and ${}^{16}\mbox{O} ({}^{12}\mbox{C}, \mbox{n}){}^{27}\mbox{Si} (\mbox{n}, \gamma) {}^{28}\mbox{Si}$.  Since the neutron capture processes on the intermediate nuclei happen at a fast timescale, the rates
including neutrons are approximated by assuming the subsequent neutron capture is instantaneous as ${}^{12}\mbox{C} ({}^{12}\mbox{C}, \gamma) {}^{24}\mbox{Mg}$,  ${}^{16}\mbox{O} ({}^{16}\mbox{O}, \gamma) {}^{32}\mbox{S}$, and ${}^{16}\mbox{O} ({}^{12}\mbox{C}, \gamma) {}^{28}\mbox{Si}$, and the network does not include neutrons. We also note that their reverse rates are not included due to their negligible effects at $T \sim 10^9$ K.  Finally, we included the additional rates ${}^{14}\mbox{N}(\alpha,\gamma){}^{18}\mbox{F}(\alpha, \mbox{p}){}^{21}\mbox{Ne}$ and ${}^{12}\mbox{C}(\mbox{p}, \gamma) {}^{13}\mbox{N}(\alpha, \mbox{p}){}^{16}\mbox{O}$, discussed in \cite{Shen_2009, Weinberg_2006,Karakas_2008, fisker:2008} to bypass the comparatively slow ${}^{12}$C $\alpha$-capture process, ${}^{12}\mbox{C} (\alpha, \gamma) {}^{16}\mbox{O}$, when $T \gtrsim 10^9$ K. The first $\alpha$-capture process on ${}^{14}\mbox{N}$ and ${}^{18}\mbox{F}$ led to the production of protons that can be used for the $\alpha$ chain process on ${}^{12}\mbox{C}$. When $T \gtrsim 10^9$ K, ${}^{12}\mbox{C}(\mbox{p}, \gamma) {}^{13}\mbox{N}(\alpha, \mbox{p}){}^{16}\mbox{O}$ is expected to dominate the reactive flow towards the heavy $\alpha$ chain nuclei, which can lead to a completely different end-stage composition \citep{Weinberg_2006, fisker:2008}. Since these additional rates leave ${}^{21}\mbox{Ne}$ as the endpoint, ${}^{22}\mbox{Na}$ is added to connect all the nuclei. With all the modifications, {\tt subch\_full} has 28 isotopes and 107 rates. 
Figure~\ref{fig:networks} shows a visualization
of this network.

{\tt subch\_full\_mod} is identical to the {\tt subch\_full} network, except that the ${}^{12}\mbox{C}(\mbox{p}, \gamma) {}^{13}\mbox{N}(\alpha, \mbox{p}){}^{16}\mbox{O}$ and its reverse reactions are turned off. This is done to explore the significance of these two rates, as described in \cite{Shen_2009, Weinberg_2006, fisker:2008}.

@@

Lastly, we present {\tt subch\_simple} network, a simplification of {\tt subch\_full} network that would resemble a more similar network to {\tt aprox13}. The network omits a total of six nuclei, namely ${}^{35}\mbox{Cl}$, ${}^{39}\mbox{K}$, ${}^{43}\mbox{Sc}$, ${}^{47}\mbox{V}$, ${}^{51}\mbox{Mn}$, and ${}^{55}\mbox{Co}$, using the $(\alpha, \mbox{p})(\mbox{p}, \gamma)$ approximation. The reverse rates of all ${}^{12}\mbox{C} + {}^{12}\mbox{C}$,  ${}^{16}\mbox{O} + {}^{16}\mbox{O}$, and ${}^{16}\mbox{O} + {}^{12}\mbox{C}$ are removed since they are not present in {\tt aprox13}. 
All the forward and reverse rates of ${}^{12}\mbox{C} + {}^{20}\mbox{Ne}$ , ${}^{23}\mbox{Na}(\alpha, \gamma){}^{27}\mbox{Al}$, and ${}^{27}\mbox{Al}(\alpha, \gamma){}^{31}\mbox{P}$ are also removed to simplify the network.
After the simplifications, we now have 22 isotopes and 57 rates. See the bottom panel of Figure \ref{fig:networks} for visualization.

@@

Plasma screening is the enhancement of nuclear reaction rates due to the Coulomb coupling of the surrounding plasma electrons and ions. Plasma screening plays an important role in accurately calculating nuclear reaction rates in dense regions.
Depending on the thermodynamic conditions, 
screening can enhance the rate by several orders
of magnitude (see, e.g., \citealt{woosley-ignition}).
There are many approximations for screening in the literature, but these are not
often explored and compared in real simulations.
We consider two different screening approximations
for our XRB simulations.

A reaction rate cross section, $\sigma$, takes the form:
\begin{equation}
    \sigma(E) = \frac{S(E)}{E} e^{-2\pi \eta}
\end{equation}
where $S(E)$ contains the details of the nuclear physics, $E$ is the energy of particle collisions in the center-of-mass frame, and $\eta$, accounts for Coulomb barrier penetration due to quantum effects \citep{Newton2007}. The reaction rate, $R_{\textrm{th}}$, is found by integrating the cross-section over the Maxwellian velocity distribution.  If the nuclei involved in the reaction are present in a high-density region that is permeated with plasma particles, then the strength of the Coulomb barrier would be reduced due to the plasma screening effect since the effective charge of the fusing nuclei are reduced. The screening enhancement factor is usually expressed as
\begin{equation}
    F_{\textrm{scr}} = \exp{(h)}
\end{equation}
where $h$ is a function that characterizes the screening magnitude. Therefore, the overall screened nuclear reaction rate is defined as
\begin{equation}\label{Eq:screened_rate}
    R_{\textrm{scr}} = F_{\textrm{scr}}R_{\textrm{th}}
\end{equation}

@@

{\tt SCREEN5} is the name of a widely-circulated screening routine (originally written in Fortran) that was the original screening routine used by \castro.
The overall procedure of {\tt SCREEN5} is summarized in the appendix of \cite{Wallace:1982}. In {\tt SCREEN5}, we define $\Gamma = (2/(Z_1+Z_2))^{1/3}Z_1 Z_2 \Gamma_e$, where $\Gamma_e = e^2\sqrt[3]{(4\pi n_e/3)}/(k_BT)$ describes the thermodynamic condition at which the reaction takes place, $Z$ is the charge of the fusing nuclei, $\mu_{12}$ is the reduced mass for the two fusing nuclei, $e$ is the electron charge, $n_e$ is the electron number density, and $k_B$ is Boltzmann's constant. When the plasma screening effect is weak or $\Gamma < 0.3$, {\tt SCREEN5} utilizes the equation proposed by \cite{Graboske_1973, Dewitt_1973}, which assumes that the interacting nuclei are separated by zero distance. To account for the spatial dependence of the screening enhancement factor, a more precise description of the strong plasma screening limit is utilized when $\Gamma > 0.8$. In \cite{jancovici:1977}, a quadratic dependence of the separation distance between the interacting nuclei was shown. This idea was applied to a one-component plasma by \cite{alastuey:1978}. By following a similar procedure outlined in \cite{itoh:1979}, the screening routine for one-component plasma can be extended to a multi-component plasma, which is suitable for a general mixture of ions. Finally, in
the intermediate screening regime, $0.3 < \Gamma < 0.8$, a weighted average between the weak and strong screening enhancement functions is used.

@@

The default method for coupling hydrodynamics and nuclear reactions in {\castro} is the classic Strang-splitting method \citep{strang:1968}. This operator-splitting approach considers the hydrodynamics and nuclear reactions to be independent processes. 
The overall procedure of Strang-splitting is as follows: first, the reactive part of the system is integrated over half of the timestep, $\Delta t/2$, using a standard ODE solver to determine the solution of an intermediate state, $\mathcal{U}^\star$, which is centered in time. Advection then
evolves $\mathcal{U}^\star$ through a full timestep $\Delta t$
yielding the state $\mathcal{U}^{\star\star}$.  Finally,
the second half-timestep of burning is done for $\Delta t/2$ starting
with $\mathcal{U}^{\star\star}$ to obtain the final state $\mathcal{U}^{n+1}$. By applying the advection and hydrodynamic operator to an intermediate state that has already incorporated the nuclear reaction effect over $\Delta t/2$, an indirect coupling is achieved between the two operations and achieves a second-order accuracy in time.  The Strang-splitting implementation
in \castro\ was described in \cite{castro_strang}.

@@

A simplfiied-SDC algorithm was introduced in \castro\ in \cite{castro_simple_sdc}.  The simplified-SDC algorithm explicitly couples reactions and hydrodynamics by including a reactive source in the hydrodynamics
interface state prediction and including an advective source in the reaction ODE integration.  
The simplified-SDC scheme offers advantages over the traditional Strang-splitting method even though they both achieve second-order accuracy in time. Specifically, the simplified-SDC scheme provides a direct coupling between hydrodynamics and nuclear reactions, which eliminates the splitting error associated with operator splitting. It also reduces the stiffness of solving reaction equations, leading to reduced computational expenses under extreme thermodynamic conditions.  In \cite{castro_simple_sdc}, it was observed that the simplified-SDC method
provides a much more accurate evolution than the Strang-split method when evolving He and C detonations
in white dwarfs.

@@

We present a total of seven XRB simulations using different combinations of reaction networks, time evolution methods, and screening routines. In order to investigate the sensitivity of the propagating flame to nuclear reactions, the default screening routine, {\tt SCREEN5}, and Strang-splitting are used with the four different networks: {\tt aprox13}, {\tt subch\_full}, {\tt subch\_full\_mod}, {\tt subch\_simple}. We replaced the {\tt SCREEN5} screening routine with {\tt CHUGUNOV2007} for the {\tt aprox13} model with Strang-splitting to investigate the difference in their performance. Lastly, in order to test the performance of the simplified SDC method, we ran two additional simulations using {\tt aprox13} and {\tt subch\_full} with simplified SDC instead of Strang-splitting. The overall summary of the simulations is shown in Table \ref{Tab:settings}.  We will
refer to the simulations by the names in the table
in the following discussion.

@@

Figure \ref{fig:network_abar_50ms} shows a comparison of the mean molecular weight, $\Bar{A}$, for the four networks at $t = 50$ ms. Regions with a larger $\Bar{A}$ represent the ash, tracing
the burning in the accreted layer. One immediate feature is the similarity of the ash structure between {\tt aprox13} and {\tt subch\_full\_mod}, as well as between {\tt subch\_full} and {\tt subch\_simple}. For {\tt subch\_full} and {\tt subch\_simple}, there is a thicker overall ash structure on the surface indicating much more vigorous burning. The sudden increase in the ash height from $r = 5 \times 10^4$ cm to $10^5$ cm for these two simulations further implies a non-uniform burning has taken place, unlike in {\tt aprox13} and {\tt subch\_full\_mod}. The darker color means that the ash in {\tt subch\_full} and {\tt subch\_simple} is composed of heavier nuclei suggesting a faster reactive flow burning to the heavier nuclei compared to the other two models. The ash also extends further out suggesting a faster flame speed compared to {\tt aprox13} and {\tt subch\_full\_mod}. 
The energy generation rate (shown in Figure \ref{fig:network_enuc_50ms}) shows the same trends: {\tt subch\_full} and {\tt subch\_simple} clearly possess a higher $\dot{e}_{\textrm{nuc}}$ in both magnitude and region coverage compared to the other two. 
% We continue to see the similar behavior of the 4 different simulation models in Figure \ref{fig:network_z_50ms}, which shows the velocity induced by the Coriolis force going out of the plane.

@@

In order to quantify how the flame changes over time, we look at the
density-weighted profile of temperature and energy generation rate in the burning, following the procedure in \citet{harpole:2021}. 
We selected cells that are in the 99th percentile or higher for temperature or energy generation rate and compute a density-weighted average of temperature and energy generation rate:
\begin{equation}\label{Eq:weighted_equation}
    \left<Q\right>_w = \frac{\sum\limits_{c_i}^{} \rho(c_i) Q(c_i)}{\sum\limits_{c_i} \rho(c_i)}; c_i \in C_{99}(Q)
\end{equation}
where $\left<Q\right>_w$ is the weighted quantity, $C_{99}(Q)$ are cells where the quantity, $Q$, is in the 99th percentile or higher, and $\rho(c_i)$ and $Q(c_i)$ are the density and the quantity in $c_i$ cell.
Figure \ref{fig:network_time_profile} shows the resulting profiles.

The temperature and energy generation rate profiles for {\tt subch\_full} and {\tt subch\_simple} are nearly identical.  As the primary distinction between these two is the $(\alpha, \mbox{p})(\mbox{p}, \gamma)$ approximation for heavier nuclei, we can conclude that this approximation remains accurate in the context of XRB.
